Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-04 analysis/8-sim-extinction-risk.Rmd
Stop dividing by N where we shouldn't

```{r}
library("skewt")
perc_downs <- function(df, gamma) {
  N <- 1e6
  proc_error <- rskt(N, df = df, gamma = gamma)
  # hist(proc_error)
  l <- qnorm(0.0001, 0, sd = 1)
  u <- qnorm(0.9999, 0, sd = 1)
  downs <- sum(proc_error < l) / N
  ups <- sum(proc_error > u) / N
  downs / (downs + ups)
}
perc_downs(df = 2, gamma = 0.75)
perc_downs(df = 3, gamma = 0.75)
```

>>>>

```{r}
library("skewt")
perc_downs <- function(df, gamma) {
  N <- 1e6
  proc_error <- rskt(N, df = df, gamma = gamma)
  # hist(proc_error)
  l <- qnorm(0.0001, 0, sd = 1)
  u <- qnorm(0.9999, 0, sd = 1)
  downs <- sum(proc_error < l)
  ups <- sum(proc_error > u)
  downs / (downs + ups)
}
perc_downs(df = 2, gamma = 0.75)
perc_downs(df = 3, gamma = 0.75)
```
